\phantomsection
\begin{thebibliography}{21}

\bibitem{spec}
James Gosling, Bill Joy, Guy Steele, Gilad Bracha, Alex Buckley. \textit{The Java® Language Specification.} The Java® Language Specification. Oracle America, Inc., 13 Feb. 2015. Web. 12 Dec. 2016. <\url{http://docs.oracle.com/javase/specs/jls/se8/html/index.html}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/specs/jls/se8/html/index.html}









\bibitem{gosling}
Gosling, James, Bill Joy, Guy Steele, Gilad Bracha, and Alex Buckley. \textit{The Java® Virtual Machine Specification.} The Java® Virtual Machine Specification. Oracle America, Inc, 28 Feb. 2013. Web. 12 Aug. 2014. <\url{https://docs.oracle.com/javase/specs/jvms/se7/html/}>.

\qrcode[height=.5in]{https://docs.oracle.com/javase/specs/jvms/se7/html/}


\bibitem{api}
\textit{Java Platform SE 7.} Java Platform SE 7. Oracle, n.d. Web. 12 Dec. 2014. <\url{http://docs.oracle.com/javase/7/docs/api/}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/7/docs/api/}

\bibitem{tutorial}
\textit{Trail: Learning the Java Language.} The Java™ Tutorials. Oracle, n.d. Web. 12 Dec. 2014. <\url{https://docs.oracle.com/javase/tutorial/java/index.html}>.

\qrcode[height=.5in]{https://docs.oracle.com/javase/tutorial/java/index.html}

\bibitem{nicholas}
Nicholas, Ethan. \textit{Understanding Weak References.} Understanding Weak References. Java.net, 4 May 2006. Web. 13 Dec. 2014. <\url{https://weblogs.java.net/Fblog/2006/05/04/understanding-weak-references}>.

\qrcode[height=.5in]{https://weblogs.java.net/Fblog/2006/05/04/understanding-weak-references}

\bibitem{reference}
\textit{Package java.lang.ref.} Java.lang.ref (Java Platform SE 7 ). Oracle, n.d. Web. 13 Dec. 2014. <\url{http://docs.oracle.com/javase/7/docs/api/java/lang/ref/package-summary.html}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/7/docs/api/java/lang/ref/package-summary.html}

\bibitem{garbagecollection}
\textit{Java Garbage Collection Basics.} Java Garbage Collection Basics. Oracle, n.d. Web. 13 Dec. 2014. <\url{http://www.oracle.com/webfolder/technetwork/tutorials/obe/java/gc01/index.html}>.

\qrcode[height=.5in]{http://www.oracle.com/webfolder/technetwork/tutorials/obe/java/gc01/index.html}

\bibitem{java7}
\textit{Java SE 7 Features and Enhancements.} Java SE 7 Features and Enhancements. Oracle, n.d. Web. 13 Dec. 2014. <\url{http://www.oracle.com/technetwork/java/javase/jdk7-relnotes-418459.html#jdk7changes}>.

\qrcode[height=.5in]{http://www.oracle.com/technetwork/java/javase/jdk7-relnotes-418459.html#jdk7changes}

\bibitem{gcergo}
\textit{Garbage Collector Ergonomics.} Garbage Collector Ergonomics. Oracle, n.d. Web. 13 Dec. 2014. <\url{http://docs.oracle.com/javase/7/docs/technotes/guides/vm/gc-ergonomics.html}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/7/docs/technotes/guides/vm/gc-ergonomics.html}

\bibitem{list}
\textit{Interface List<E>} Java™ Platform, Standard Edition 8
API Specification. Oracle, n.d. Web. 7 Dec. 2016. <\url{http://docs.oracle.com/javase/8/docs/api/java/util/List.html}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/8/docs/api/java/util/List.html}

\bibitem{map}
\textit{Interface Map<E>} Java™ Platform, Standard Edition 8
API Specification. Oracle, n.d. Web. 7 Dec. 2016. <\url{https://docs.oracle.com/javase/8/docs/api/java/util/Map.html}>.

\qrcode[height=.5in]{https://docs.oracle.com/javase/8/docs/api/java/util/Map.html}

\bibitem{set}
\textit{Interface Set<E>} Java™ Platform, Standard Edition 8
API Specification. Oracle, n.d. Web. 7 Dec. 2016. <\url{https://docs.oracle.com/javase/8/docs/api/java/util/Set.html}>.

\qrcode[height=.5in]{https://docs.oracle.com/javase/8/docs/api/java/util/Set.html}

\bibitem{error}
\textit{Class Error} Java™ Platform, Standard Edition 8
API Specification. Oracle, n.d. Web. 7 Dec. 2016. <\url{http://docs.oracle.com/javase/8/docs/api/java/lang/Error.html}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/8/docs/api/java/lang/Error.html}

\bibitem{exception}
\textit{Class Exception} Java™ Platform, Standard Edition 8
API Specification. Oracle, n.d. Web. 7 Dec. 2016. <\url{http://docs.oracle.com/javase/8/docs/api/java/lang/Exception.html}>.

\qrcode[height=.5in]{http://docs.oracle.com/javase/8/docs/api/java/lang/Exception.html}

\bibitem{runtimeexception}
\textit{Unchecked Exceptions — The Controversy} The Java™ Tutorials. Oracle, n.d. Web. 7 Dec. 2016. <\url{https://docs.oracle.com/javase/tutorial/essential/exceptions/runtime.html}>.

\qrcode[height=.5in]{https://docs.oracle.com/javase/tutorial/essential/exceptions/runtime.html}


\bibitem{codesmells}
\textit{Smells to Refactorings -- Quick Reference Guide} Industrial Logic, n.d. Web. 14 Dec. 2016. <\url{http://www.industriallogic.com/wp-content/uploads/2005/09/smellstorefactorings.pdf}>.

\qrcode[height=.5in]{http://www.industriallogic.com/wp-content/uploads/2005/09/smellstorefactorings.pdf}

\bibitem{referenceorvalue}
\textit{Does Java pass by reference or pass by value?} Java World, n.d. Web. 14 Dec. 2016. <\url{http://www.javaworld.com/article/2077424/learn-java/does-java-pass-by-reference-or-pass-\hyp{}by-value.html}>.

\qrcode[height=.5in]{http://www.javaworld.com/article/2077424/learn-java/does-java-pass-by-reference-or-pass-by-value.html}


\bibitem{slf4j}
\textit{Simple Logging Facade for Java (SLF4J)} slf4j.org, n.d. Web. 14 Dec. 2016. <\url{http://www.slf4j.org/}>.

\qrcode[height=.5in]{http://www.slf4j.org/}

\bibitem{simplelogger}
\textit{Class SimpleLogger} SLF4J 1.7.22 API, n.d. Web. 14 Dec. 2016. <\url{http://www.slf4j.org/api/org/slf4j/impl/SimpleLogger.html}>.

\qrcode[height=.5in]{http://www.slf4j.org/api/org/slf4j/impl/SimpleLogger.html}

\bibitem{slf4jmanual}
\textit{SLF4J user manual} slf4j.org, n.d. Web. 14 Dec. 2016. <\url{http://www.slf4j.org/manual.html}>.

\qrcode[height=.5in]{http://www.slf4j.org/manual.html}

\bibitem{level}
\textit{Class Level} Java™ Platform, Standard Edition 8
API Specification. Oracle, n.d. Web. 14 Dec. 2016. <\url{https://docs.oracle.com/javase/8/docs/api/java/util/logging/Level.html}>.

\qrcode[height=.5in]{https://docs.oracle.com/javase/8/docs/api/java/util/logging/Level.html}
\end{thebibliography}
