\section{Methods, Encapsulation and Inheritance}

some description

\subsection{Composition, Inheritance, and Static Method Calls}
\textit{Show how to use a common piece of logic from two different classes, in three different ways: 1) by composition, 2) by inheritance, and 3) by static method calls, discuss the tradeoffs
for example: 
\begin{itemize}
\item two different classes that write a message to a file, one in XML, one in line-oriented text, but both need to reuse logic to open the file in the same way
\end{itemize}
}

some text


\subsection{Constructors}
\textit{Create and overload constructors -- Create a class that has 4 fields and construct the class with variations of one required field and the others are optional.  Use constructor chaining as an example.}

some text

\subsection{Encapsulation}
\textit{Apply encapsulation principles to a class -- Show an example of good encapsulation.  Show a bad example of encapsulation and explain why.  Additionally explain access modifiers and how they can be used as part of the class encapsulation.}

some text

\subsection{Object References and Primitives}
\textit{Determine the effect upon object references and primitive values when they are passed  into methods that change the values -- Create a method 3 parameters, one is parameter is pass by value, one is passed by reference and one with the keyword final.  Explain each and what the effects in side the method that changes each one.
}

some text


\subsection{Access Modifiers}
\textit{Write code to show how access modifiers work: private, protected, and public, talk about why you would use each of these.}

some text



\subsection{Virtual Method Invocation}
\textit{Write code to show how virtual method invocation lets one implementation be swapped for another.}

some text


\subsection{Casting}
\textit{Write code that uses the instanceof operator and show how casting works.}

some text


\subsection{Overridden Methods}
\textit{Show how to override a method in a subclass, talk about plusses and minuses in doing so.}

some text

\subsection{Overloaded Constructors and Methods}
\textit{Show how to overload constructors and methods, talk about plusses and minuses in doing so.}

some text