\phantomsection
\bibliographystyle{unsrt}

\begin{thebibliography}{9}

\bibitem{gosling}
   Gosling, James, Bill Joy, Guy Steele, Gilad Bracha, and Alex Buckley. \textit{The Java® Virtual Machine Specification.} The Java® Virtual Machine Specification. Oracle America, Inc, 28 Feb. 2013. Web. 12 Aug. 2014. <https://docs.oracle.com/javase/specs/jvms/se7/html/>.

\bibitem{lindholm}
Lindholm, Tim, Frank Yellin, Gilad Bracha, and Alex Buckley. \textit{The Java® Virtual Machine Specification.} The Java® Virtual Machine Specification. Oracle America, Inc., 28 Feb. 2013. Web. 12 Dec. 2014. <https://docs.oracle.com/javase/specs/jvms/se7/html/>.

\bibitem{api}
\textit{Java Platform SE 7.} Java Platform SE 7. Oracle, n.d. Web. 12 Dec. 2014. <http://docs.oracle.com/javase/7/docs/api/>.

\bibitem{tutorial}
\textit{Trail: Learning the Java Language.} The Java™ Tutorials. Oracle, n.d. Web. 12 Dec. 2014. <https://docs.oracle.com/javase/tutorial/java/index.html>.

\bibitem{nicholas}
Nicholas, Ethan. \textit{Understanding Weak References.} Understanding Weak References. Java.net, 4 May 2006. Web. 13 Dec. 2014. <https%3A%2F%2Fweblogs.java.net%2Fblog%2F2006%2F05%2F04%2Funderstanding-weak-references>.

\bibitem{reference}
\textit{Package java.lang.ref.} Java.lang.ref (Java Platform SE 7 ). Oracle, n.d. Web. 13 Dec. 2014. <http://docs.oracle.com/javase/7/docs/api/java/lang/ref/ package-summary.html>.

\bibitem{garbagecollection}
\textit{Java Garbage Collection Basics.} Java Garbage Collection Basics. Oracle, n.d. Web. 13 Dec. 2014. <http://www.oracle.com/webfolder/technetwork/tutorials/ obe/java/gc01/index.html>.




\end{thebibliography}